### 2013-09-18 chi2014/introduction.tex
small edit

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model. The rates of novel ideas and categories of ideas decrease exponentially.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. 
\item We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 15).
\end{itemize}

>>>>

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. 
\item We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 15).
\end{itemize}
